Function

### 2021-06-15 Function.Rmd
initial work on function

```{r}
#Goal: Pr(Signature|Mutation) in a particular sample

Bayes_function <- function(mutation, process, sample, nmf_matrix, mutation_matrix){
  #Pr(Mutation|Signature)
  a <- nmf_matrix$signatures[mutation,process]/sum(nmf_matrix$signatures[,process])
  #Pr(Signature)
  b <- nmf_matrix$contribution[process,sample]/sum(nmf_matrix$contribution[,sample])
  #Pr(Mutation)
  c <- mutation_matrix[mutation, sample]/sum(mutation_matrix[,sample])
  #Bayes Formula Calculation
  prob <- a*b/c
  return(prob)
}
```

@@

>>>>

```{r}
#Goal: Pr(Signature|Mutation) in a particular sample
#Change name for nmf_matrix
#Split denominator into two pieces, add a parameter for which method we use
#One function that doesn't need mutational signature
Bayes_function <- function(mutation, signature, sample, nmf_matrix, mutation_matrix){
  #Pr(Mutation|Signature)
  a <- nmf_matrix$signatures[mutation,signature]/sum(nmf_matrix$signatures[,signature])
  #Pr(Signature)
  b <- nmf_matrix$contribution[signature,sample]/sum(nmf_matrix$contribution[,sample])
  #Pr(Mutation)
  c <- mutation_matrix[mutation, sample]/sum(mutation_matrix[,sample])
  #Bayes Formula Calculation
  prob <- a*b/c
  return(prob)
}
```

@@

```{r}
plot_96_profile(nmf_res$signatures)
```
